\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-07-21 tex/abstract.tex
update abstract

\begin{abstract}
The relationship between network topology and system dynamics has significant implications for unifying our understanding of the interplay among metabolic, gene-regulatory, and ecosystem network architecures. Here we analyze the stability and robustness of a large class of dynamics on such networks. We determine the probability distribution of robustness as a function of network topology and show that robustness is classified by the number of links between modules of the network. We also demonstrate that permutation of these modules is a fundamental symmetry of dynamical robustness. Analysis of these findings leads to the conclusion that the most robust systems have the most hierarchical structure. This relationship provides a means by which evolutionary selection for a purely dynamical phenomenon may shape network architectures across scales of the biological hierarchy.
\end{abstract}

>>>>

\begin{abstract}
The relationship between network topology and system dynamics has significant implications for unifying our understanding of the interplay among metabolic, gene-regulatory, and ecosystem network architecures. Here we analyze the stability and dynamical robustness of a large class of dynamics on such networks, the latter considered to occur over evolutionary timescales. We determine the probability distribution of dynamical robustness as a function of network topology and show that dynamical robustness is classified by the number of links between modules of the network. We also demonstrate that permutation of these modules is a fundamental symmetry of dynamical robustness. Analysis of these findings leads to the conclusion that the most dynamically robust systems correspond to the most hierarchical connectivity of these modules. This relationship provides a means by which evolutionary selection for a purely dynamical phenomenon may shape network architectures across scales of the biological hierarchy.
\end{abstract}
